Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-09 p2/axiom-proof.tex
Added TODO

In this section we derive the \namecrefs{ax_separate_commute} listed in
\cref{rules_lemma} from our filesystem model.
For the purposes of the proofs we extend the notion of filesystems 
to the full set of functions mapping $\setn$ to $\setv$, even if they
do not have the tree property.
This is so that we can describe the values they would acquire under certain nodes,
and pinpoint where they may be violating the tree property.
If they do, we continue to say that the filesystem is broken,
and say that the filesystem is \emph{broken at $n$} if 
$n$ is not a dictionary, but has at least one non-empty child.
We continue to require that filesystems are not empty at finitely many nodes.

>>>>

In this section we derive the \namecrefs{ax_separate_commute} listed in
\cref{rules_lemma} from our filesystem model.
For the purposes of the proofs we extend the notion of filesystems % TODO review if needed
to the full set of functions mapping $\setn$ to $\setv$, even if they
do not have the tree property.
This is so that we can describe the values they would acquire under certain nodes,
and pinpoint where they may be violating the tree property.
If they do, we continue to say that the filesystem is broken,
and say that the filesystem is \emph{broken at $n$} if 
$n$ is not a dictionary, but has at least one non-empty child.
We continue to require that filesystems are not empty at finitely many nodes.
